Nock for Everyday Coders

### 2025-08-28 mss.tex
Post

In English, this means: ``ignore the subject `a`, and just return everything after the \lstinline[style=inlinecode]{@1@} exactly as it is.

>>>>

In English, this means: ``ignore the subject \lstinline[style=inlinecode]{a}, and just return everything after the \lstinline[style=inlinecode]{@1@} exactly as it is.
